#Reproducible Research : Assignment 1
# 1
###Loading and preprocessing the data

```{r,echo  = TRUE}
unzip("C:/Users/Alket/Documents/repdata-data-activity.zip")
activity <- read.csv("activity.csv")
```
### Structure of the activity data.frame
```{r, echo = TRUE}
str(activity)
```

# 2
### The total number of steps is calculated as bellow : 
```{r,echo  = TRUE}
totalSteps <- tapply(activity$steps, activity$date, sum, na.rm=T)
```
#Histogram

### The histogram of total number of steps : 
```{r,echo = TRUE}
hist(totalSteps, breaks = 10)
```

# Mean

### The mean calculated on the total number of steps 
```{r,echo = TRUE}
stepMean <- mean(totalSteps)
stepMean
```

#Mediana
### The mediana calculated on the total number of steps 
```{r, echo = TRUE}
stepMedian <- median(totalSteps)
stepMedian
```

# 3
#What is the average daily activity pattern?
### Loading the necessary  R library ggplot2

```{r, echo = TRUE}
library(ggplot2)
```
### Put in averageDaily the aggregated result to be ploted as timeserie
```{r, echo = TRUE}
averageDaily <- aggregate(x = list(steps = activity$steps), by = list(interval = activity$interval), FUN = mean, na.rm = TRUE)
```

### The timeserie graph of the pattern
```{r, echo = TRUE}
ggplot(data = averageDaily, aes(x = interval,y = steps)) + geom_line()+xlab("5-minute interval") + ylab("average number of steps taken")
```

### The maximum number of steps 
```{r, echo = TRUE}
max <- averageDaily[which.max(averageDaily$steps), ]
max
```

#4
# Imputing missing values: devising the strateghy 

### the total number of missing values: 
```{r, echo = TRUE}
sum(is.na(activity))
```


### The strateghy for filling the missing number of values will be as follows: the missing values will be filled with the average of the existing  values

#The function for filling the missing values

```{r, echo = TRUE}

fillValues <- function(steps, interval) {
    filled <- NA
    if (!is.na(steps)) 
        filled <- c(steps) else filled <- (averageDaily[averageDaily$interval == interval, "steps"])
    return(filled)
}
```
#Create a new dataset that will have the missed data filled in with the average value 
```{r}
filledData <- activity
filledData$steps <- mapply(fillValues, filledData$steps, filledData$interval)
totalSteps <- tapply(filledData$steps, filledData$date, FUN = sum)
```

# the histogram of the new dataset with the values filled in 

```{r, echo = TRUE}
hist(totalSteps, breaks = 10)
```

knit2html()
### the mean of total number of steps after filling the dataset

```{r, echo = TRUE}
meanTotalSteps <- mean(totalSteps)
meanTotalSteps
```
### the meadiana of tot number of steps after filling the dataset 
```{r, echo = TRUE}
medianTotalSteps <- median(totalSteps)
medianTotalSteps

```

# the difference between patterns ....
